Table

### 2025-09-23 manuscript/manuscript.qmd
table text size

The Water Framework Directive (WFD) indicators use aggregation pathway 5 (@fig-pathways), 
with truncation, scaling, and transformation, in that order.
The value obtained after the first two steps is called an EQR (ecological quality ratio), 
and the value obtained after the third step is called nEQR 
(normalised EQR, and true indicator values *sensu* SEEA EA).
Spatial aggregation, the way that we use the term here, is not done for the WFD.
Instead, the aggregated reporting metric is the proportion of water bodies in each of the five condition classes 
("bad", "poor", "moderate", "good", "high"), 
separated by the non-terminal reference levels. \

>>>>

The Water Framework Directive (WFD) indicators use aggregation pathway 5 (@fig-pathways), 
with truncation, scaling, and transformation, in that order.
The value obtained after the first two steps is called an EQR (ecological quality ratio), 
and the value obtained after the third step is called nEQR 
[normalised EQR, and true indicator values *sensu* SEEA EA; @van_de_bund_ecological_2007].
Spatial aggregation, the way that we use the term here, is not done for the WFD.
Instead, the aggregated reporting metric is the proportion of water bodies in each of the five condition classes 
("bad", "poor", "moderate", "good", "high"), 
separated by the non-terminal reference levels. \

### 2025-09-23 manuscript/terms_table.qmd
table text size

    **Truncation** means to recode scaled variable above 1 to become 1, and values below 0 to become 0.**Transformation** means to adjust the indicator scale to reflect potentially nonlinear relationships between the variable and ecosystem condition. This is commonly done by anchoring specific variable values to predefined class boundaries (sensu WFD) which we call reference levels [@czúcz; @jakobsson_setting_2020], but may also be done without explicit reference levels, for example by using a sigmoid or exponential transformation [@mienna2024].

@@

    Y = "Also called vertical aggregation. In the case of ECA, this refers to an aggregation of two or more indicators into a composite index (_plural_: indices)."

@@

flextable(terms) |>
  width(j = 1, width = 1) |>     # Relative width
  width(j = 2, width = 5) |>     # Relative width  
  valign(j = 1:2, valign = "top", part = "all") |>
  ftExtra::colformat_md(j = 2)

>>>>

    **Truncation** means to recode scaled variable above 1 to become 1, and values below 0 to become 0.**Transformation** means to adjust the indicator scale to reflect potentially nonlinear relationships between the variable and ecosystem condition. This is commonly done by anchoring specific variable values to predefined class boundaries [sensu WFD; @directiv2000] which we call reference levels [@czúcz; @jakobsson_setting_2020], but may also be done without explicit reference levels, for example by using a sigmoid or exponential transformation [@mienna2024].

@@

    Y = "Also called vertical aggregation. In the case of ECA, this refers to an aggregation of two or more indicators into a composite **index** (_plural_: **indices**)."

@@

flextable(terms) |>
  width(j = 1, width = 1) |>     
  width(j = 2, width = 5) |>     
  valign(j = 1:2, valign = "top", part = "all") |>
  ftExtra::colformat_md(j = 2) |>
  fontsize(size = 9, part = "all")
